%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Two Column One Page Curriculum Vitae
% LaTeX Template
% Version 1.1 (24/1/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro (The CV Inn)
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Font size - 10pt, 11pt or 12pt

\usepackage[hmargin=1.25cm, vmargin=1.5cm]{geometry} % Document margins

\usepackage{marvosym} % Required for symbols in the colored box
\usepackage{ifsym} % Required for symbols in the colored box

\usepackage[usenames,dvipsnames]{xcolor} % Allows the definition of hex colors

% Fonts and tweaks for XeLaTeX
\usepackage{fontspec,xltxtra,xunicode}
\defaultfontfeatures{Mapping=tex-text}
\setmainfont[Mapping=tex-text]{Times New Roman} % Main document font
\setsansfont[Scale=MatchLowercase,Mapping=tex-text]{Times New Roman} % Font for your name at the top
%\setmonofont[Scale=MatchLowercase]{Andale Mono}

% Colors for links, text and headings
\usepackage{hyperref}
\definecolor{linkcolor}{HTML}{506266} % Blue-gray color for links
\definecolor{shade}{HTML}{F5DD9D} % Peach color for the contact information box
\definecolor{text1}{HTML}{2b2b2b} % Main document font color, off-black
\definecolor{headings}{HTML}{701112} % Dark red color for headings
% Other color palettes: shade=B9D7D9 and linkcolor=A40000; shade=D4D7FE and linkcolor=FF0080

\hypersetup{colorlinks,breaklinks, urlcolor=linkcolor, linkcolor=linkcolor} % Set up links and colors

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
% Headers and footers can be added with the \lhead{} \rhead{} \lfoot{} \rfoot{} commands
% Example footer:
%\rfoot{\color{headings} {\sffamily Last update: \today}. Typeset with Xe\LaTeX}

\renewcommand{\headrulewidth}{0pt} % Get rid of the default rule in the header

\usepackage{titlesec} % Allows creating custom \section's

% Format of the section titles
\titleformat{\section}{\color{headings}
\scshape\Large\raggedright}{}{0em}{}[\color{black}\titlerule]

\titlespacing{\section}{0pt}{0pt}{5pt} % Spacing around titles

\begin{document}

\color{text1} % Sets the default text color for the whole document to the color defined as 'text1'

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

\par{\centering{\sffamily\Huge Mason Egger}\\ % Your name
{\color{headings}\fontspec[Variant = 2]{Times New Roman} Software Developer, System 
Administrator, System 
Engineer}\\[15pt]\par} 
	
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.5\textwidth} % Start the left-hand side of the page
\vspace{0pt} % Trick for alignment
	
%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------
\section{About Me}
Experienced system administrator with an extensive object-oriented development background. Passionate worker and proven leader with excellent 
time/project/priority management skills; driven to succeed at any task. Extensive background working in group projects and independently, along with 
great communication skills both oral and documented. Capable learner can rapidly close any  knowledge gap. Multiplatform experience from 
Windows/Mac/Linux to less common Unix based operating systems.

%----------------------------------------------------------------------------------------
%       WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Work Experience} 

%------------------------------------------------
% WORK EXPERIENCE 1
%------------------------------------------------

{\raggedleft\textsc{Current, from June 2012}\par}

{\raggedright\large Undergraduate Instructional Assistant\\
\textit{Department of Computer Science, Texas State University}\\[5pt]}

\normalsize{Lab Instructor and tutor tasked with tutoring students in a wide range of subjects and instructing course specific labs. Designed an accelerated curriculum for the advanced introductory course. Lead a team tasked with designing new software and utilities for use by faculty, staff, and students. Managed multiple departmental servers. Created automated solutions for departmental problems. Examples would be a multi-OS netboot system, a homework upload solution, automated domain join tool, etc.}\\

%------------------------------------------------
% WORK EXPERIENCE 2
%------------------------------------------------

{\raggedleft\textsc{Current, from January 2014}\par}

{\raggedright\large Owner, Developer\\
\textit{Egger Consulting}\\[5pt]}

\normalsize{Freelance developer and system administrator tasked with designing multiple applications and systems from web based registration forms to advanced network layouts and tools. Install security systems such as cameras and built websites}\\



%------------------------------------------------
% WORK EXPERIENCE 3
%------------------------------------------------

{\raggedleft\textsc{August 2014 - December 2014}\par}

{\raggedright\large Undergraduate Research Assistant\\
\textit{Department of Computer Science, Texas State University}\\[5pt]}

\normalsize{Researched secure distributed programming on mobile phones using OSGi/rOSGi. Tools used: Eclipse, Wireshark, Linux}\\


%----------------------------------------------------------------------------------------
% PROJECTS
%----------------------------------------------------------------------------------------
\section{Projects}

{\raggedright\large Hybrid Cloud Network, Netboot, Solera NFC Solutions\\}

\normalsize{For a complete list of projects, visit \href{http://www.masonegger.com}{www.masonegger.com}}\\

\end{minipage} % End the left-hand side of the page
\hfill
\begin{minipage}[t]{0.44\textwidth} % Start the right-hand side of the page
\vspace{0pt} % Trick for alignment

%----------------------------------------------------------------------------------------
%	COLORED BOX
%----------------------------------------------------------------------------------------

\colorbox{shade}{\textcolor{text1}{
\begin{tabular}{c|p{7cm}}
%\raisebox{-4pt}{\textifsymbol{18}} & 900 Peques St. Apt. 2302 San Marcos, TX \\ % Address
\raisebox{-3pt}{\Mobilefone} & (512)387-0297 \\ % Phone number
\raisebox{-1pt}{\Letter} & \href{mailto:mason@masonegger.com}{mason@masonegger.com} \\ % Email address
\Keyboard & \href{http://www.masonegger.com}{http://www.masonegger.com} \\ % Website
\end{tabular}
}
}\\[10pt]

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS
%----------------------------------------------------------------------------------------

\section{Skills} 

\begin{tabular}{rl}
Languages/Frameworks
& \textsc{Java}, \textsc{C++}, \textsc{C}, \textsc{Perl}, \textsc{Python},\\ 
& \textsc{Powershell}, \textsc{VBScript}, \textsc{Django} \\
& \textsc{Batch}, \textsc{Bash}, \textsc{MySQL}, \textsc{HTML}\\
Operating Systems
& \textsc{Windows}, \textsc{OpenBSD}, \textsc{FreeBSD}, \\
& \textsc{Linux(RHEL, CentOs, Ubuntu, Fedora)} \textsc{OS X}\\
Network
& \textsc{DNS}, \textsc{DHCP}, \textsc{Routing}, \textsc{VPN}\\
Network Administration
& \textsc{Database Design}, \textsc{MVC Design}, \\
& \textsc{LDAP}, \textsc{Active Directory},\\
& \textsc{Group Policy}, \textsc{Virtualization}, \\
& \textsc{Apache}, \textsc{Nginx}, \textsc{WireShark}, \\
& \textsc{NMap} \\ 
\end{tabular}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{Education} 

\begin{tabular}{rl} % Start a table with two columns, one for dates and one for qualifications

%------------------------------------------------
% EDUCATION 1
%------------------------------------------------

2011 -- \textsc{Present} & \textbf{Bachelor of Science} \\ 
& \textsc{Computer Science} \\ 
& \textit{Texas State University}\\
&\\

%------------------------------------------------
% GPA
%------------------------------------------------
& \large GPA: \textit{3.32} \\
& Anticipated Graduation: \textit{December 2015}\\
	 
%------------------------------------------------
% EDUCATION 2
%------------------------------------------------
\textit{Other Education} \\
2011 -- \textsc{Present} & \textbf{Bachelor of Arts} \\ 
& \textsc{Music}, \textit{Trombone}\\ 
& \textit{Texas State University}\\ \\

%----------------------------------------------------------------------------------------

\end{tabular}

%----------------------------------------------------------------------------------------
%	AWARDS
%----------------------------------------------------------------------------------------

\section{Awards} 

\begin{tabular}{rl}
2015     & \textbf{Excellence in Service}\\
& \textit{Texas State University}\\ \\
2014	 & \textbf{Excellence in Teaching}\\
	 & \textbf{Undergraduate Academic Distinction}\\
& \textit{Texas State University}\\ \\

2013     & \textbf{Excellence in Service}\\
& \textit{Texas State University}\\ \\

%------------------------------------------------

2011	 & \textbf{UIL State Champion Computer Science Team}\\
& \textit{Needville High School}
\end{tabular}\\[10pt]


%----------------------------------------------------------------------------------------
%	Extra Curricular
%----------------------------------------------------------------------------------------

\section{Extra Curricular/Leadership} 

\begin{tabular}{rl}
& Recordings: \textit{Trombones at Texas State}, \textit{Carol of the Bones} \\
& \textit{Alumni Relations Officer}, Phi Mu Alpha \\
& \textit{Vice President}, ITA Trombone Society\\
& Team Lead, \textit{Collegiate Cyber Def. Competition}\\
& Alumni, \textit{Bobcat Marching Band}\\
\end{tabular}\\[10pt]

%----------------------------------------------------------------------------------------
	
\end{minipage} % End right-hand side of the page

\newpage 
\section{Detailed Project Overview}
\textbf{Departmental NetBoot System} - In order to meet the requirements of a stable, easy to maintain lab environment, my team
 and I chose to implement an LTSP solution. Through the use of dnsmasq a chainloaded iPXE image serves up a boot menu allowing the
 user to choose an operating system. All computer information is stored in a database to enable automated imaging and domain joining
 as well as require registration for all machines within the department. \\

\textbf{Dynamic Data on NFC Chips} - This project was an experiment on the ability to assign data to physical locations and objects. 
 Since GPS technology is inaccurate within buildings and RFID chips are easily disrupted my team and I ventured into Near Field Communications.
 Each NFC chip is manufactured with a UID. We developed an Android app that scans the tag and
 queries a Django based web API with the UID information. Each chip must be registered with the API and associated with specific data.
 The API returns JSON containing the appropriate data related to the tag and the application parses it out and creates a view with the
 information.\\

\textbf{Microsoft Group Policy Password Exploit} - Setting passwords through Group Policy is an insecure means of accomplishing local account
control. This is an even greater security risk when used to set local Administrator passwords. As an assignment from my boss, I was tasked with
creating a decryption script to show the vulnerabilities of this system. All GPOs exist within the Sysvol directory on the Domain Controller
 where the Group Policy service is installed. Any authenticated user may access this folder and retrieve the XML file where the encrypted password
 is stored. This is problematic because the encryption key for this service was published and is common knowledge amongst IT Security professionals.
 With this key and a Group Policy viewer, an unprivileged user could ascertain which GPO was setting the password, navigate to the correct
 directory in the Sysvol, retrieve the hash and decrypt the password. My script allows for the user to place the hash within the code and decrypt
 the password.\\

\textbf{Hybrid Cloud Network} - In order to learn more about networking and servers I built a Hybrid Cloud/Local Network within my apartment. I
purchased older hardware and stood up a VM farm hosting many different servers. I have recently begun migrating servers to the cloud in order
to distribute my system and integrate multiple servers.
The list below illustrates my servers location and function.
\begin{itemize}
\item \textbf{Function - OS - Location}
\item Router - OpenBSD - Local
\item Bastion - OpenBSD - Local
\item Development - FreeBSD - Local
\item Active Directory - Win 2k8R2 - Local
\item DHCP - Win 2k8R2 - Local
\item Authoritative DNS - Win 2k8R2 - Local
\item Recursive DNS - Win 2k12R2 - Local
\item Penetration Testings - Kali Linux - Local
\item Reverse Proxy - FreeBSD - Local
\item Web Server 1- FreeBSD - Local
\item Web Server 2- RHEL 7 - Cloud
\end{itemize}

This project exists as a testing area for my personal endeavours and interests.  
\\

\textbf{Collegiate Cyber Defense Competition} - For the past two years I have competed in CCDC with my university. We have increasingly improved 
each year. My role on the team was to be the main person handling the Windows Servers. With tools from the Sysinternals Suite and well designed 
firewall rules I was able to defend my servers from the Red Team attacks for the majority of the competition.
\\
 
\end{document}  
